% \input{tables/full_leaderboard.tex}

\chapter{Experiments}
\label{sec:experiments}

This section provides a comprehensive quantitative analysis of \ourmodel{}
from three perspectives. 
First, we add \ourmodel{} to existing 3D detectors, showing significant improvements. We use both LiDAR-based and camera-based detectors on WOD~\cite{WOD} and AV2~\cite{wilson2023argoverse}, respectively.
Second, we compare the best version of \ourmodel{} to the state-of-the-art methods on WOD, setting a new record on the WOD leaderboard among online methods without ensembles or test-time augmentation and outperforming prior learned temporal fusion methods by a large margin.
Finally, we conduct thorough ablation studies to understand the architectural choices that make \ourmodel{} effective and the impact of different training procedures.
See \cref{sec:imp} for more implementation details.


\section{Metrics}
\label{sec:metrics}

We report the detection metrics from the official WOD leaderboard~\cite{WOD},
which include average precision (AP) and AP weighted
by heading error (APH) for vehicles (Veh.), pedestrians (Ped.), and cyclists (Cyc.).
These metrics use intersection-over-union (IoU) thresholds
of 0.7, 0.5, and 0.5, respectively.
The metrics are broken down into two levels of difficulty:
Level 1 (L1) includes only labels that have $> 5$ LiDAR points
and are not marked as ``hard'',
and Level (L2) includes all boxes that have $> 0$ LiDAR points (a superset of L1).
For camera experiments on AV2, we report the mean average precision (AP) for vehicles in the camera field of view at an IoU threshold of 0.1.
We report the macro-average over all classes if the actor class is not specified.


\section{Main Experiments}
\label{sec:main-exp}

\subsection{Augmenting off-the-shelf 3D Detectors with \ourmodel{}}
\label{sec:aug}

\Cref{tab:main-table-wod} and \cref{tab:av2-cam} show the performance of \ourmodel{} applied to off-the-shelf 3D detectors on WOD and AV2, respectively.%\thomasG{I think this sentence should be at the start of the subsection}
To show the generality of our approach, we experiment with multiple base detectors trained on different datasets and sensor modalities.
We enhanced three LiDAR-based methods with \ourmodel{} on WOD:
CenterPoint~\cite{centerpoint}
with both 1 LiDAR frame (1f) and 2 LiDAR frames (2f) as input,
HEDNet~\cite{hednet} (1f and 4f),
and SAFDNet~\cite{safdnet} (1f and 4f).
We follow their official protocols to train and evaluate all models from scratch (due to the Waymo Dataset License Agreement,
we cannot simply re-use pre-trained models).
We also enhance two camera-based methods on AV2, FCOS3D~\cite{wang2021fcos3d}
and BEVMap~\cite{chang2024bevmap},
which takes the most recent image from the front camera as input.
We use the official implementation for both FCOS3D~\cite{wang2021fcos3d} and BEVMap~\cite{chang2024bevmap}. 
See \cref{sec:off-the-shelf-imp} for implementation details.

Our model brings significant improvements to all detectors on both datasets.
These gains are largest for single-frame detectors, where the memory provides the most additional information.
The fact that the \ourmodel{}-augmented single-frame detectors are better than the multi-frame detectors clearly shows the effectiveness of our method relative to the common point aggregation approach.

\subsection{Comparison against SOTA}
\label{sec:sota}
By augmenting SAFDNet 4f with \ourmodel{},
we show in \cref{tab:full-leaderboard-all-classes} that we achieve the best performance on the WOD leaderboard\footnote{\label{wod_leaderboard2}\href{https://waymo.com/open/challenges/2020/3d-detection/}{https://waymo.com/open/challenges/2020/3d-detection/} as of submission (14/11/2024)}, among all online methods that do not use ensembles or test-time augmentation.
\Cref{tab:leaderboard-all-classes} compares \ourmodel{}
to prior learned temporal fusion methods on
the WOD validation and test set, where we achieve substantial gains.

\input{tables/full_leaderboard_all_classes.tex}

\input{tables/leaderboard_all_classes.tex}

\subsection{Ablations}
\label{sec:ablations}

\subsubsection{Effect of memory proposals and memory attention}
We ablate the different components of our memory pipeline in \cref{tab:component-ablation}.
Comparing rows 1, 2, and 5 shows that both the proposed memory attention and memory proposals have a positive effect.
This is intuitive as the memory proposals let \ourmodel{} recover from false negative detection proposals, which is complementary to memory cross-attention that allows \ourmodel{} to use all memory information for refinement (bypassing the filtering in proposal-merging). 

\subsubsection{Effect of forecasting}
Comparing rows 3 and 5 in \cref{tab:component-ablation}, we find that using trajectory forecasting to align memory proposals to the current time is important, particularly for fast-moving objects.
Without forecasting, the memory proposals from previous frames
will be far from the current position of those objects, making it challenging for the model to leverage the memory effectively.

\subsubsection{Effect of learned proposal merging}
Comparing rows 0, 4, and 5 of \cref{tab:component-ablation} we find the proposed learned rescoring of the merged detection and memory proposals is crucial for good performance.
Without it, \ourmodel{} cannot enhance the base detector (row 0) because the proposal scores from the 3D detector and memory are miss-calibrated before being post-processed in the proposal merging step (i.e., NMS).
We illustrate this in \cref{tab:proposal-eval}, where we evaluate intermediate proposals of \ourmodel{}:
(1) the detection proposals $\mathcal{P}^\mathrm{det}$,
(2) naively taking the union of the detection proposals $\mathcal{P}^\mathrm{det}$ and memory proposals $\mathcal{P}^\mathrm{mem}$ and post-processing them, %naively post-processing the merged proposals but without rescoring,
(3) the merged proposals $\mathcal{P}^\mathrm{merge}$ (which have been rescored), and
(4) after each block of the refinement transformer $\mathcal{P}^{\mathrm{ref}(1)}, \dots, \mathcal{P}^{\mathrm{ref}(I)}$.
Naively concatenating the combined proposals is much worse than the base detector because of the miss-calibrated scores.
After proposal merging, $\mathcal{P}^\mathrm{merge}$ already improves over the base detector.
Each refinement block brings further gains, illustrating the strength of our proposed refinement transformer.

\input{tables/component_ablation.tex}

\input{tables/proposal_eval.tex}

\subsubsection{Effect of self-attention}
\input{tables/supp_component_ablation.tex}
\Cref{tab:self-attention-ablation} illustrates the effect of using self-attention in the refinement transformer,
which brings a small but consistent performance improvement.
Recall that the memory cross attention only allows each query $\mathbf{Q}^{\mathrm{ref}(i)}$ to attend to
the nearest $k = 4$ memory proposals features $\mathbf{Q}^\mathrm{mem}$.
Self-attention lets queries see information from more distant memory proposals
%\thomasG{expand why}
because information about memory proposals can propagate through all query features which can be anywhere in the scene.
Furthermore, self-attention allows for modelling interactions between actors,
and prior works have shown it to improve forecasting performance~\cite{casas2024detra},
which would in turn improve \ourmodel{}'s detection performance through the memory.
Both of these factors could explain the improved performance of \ourmodel{}.

\input{sec/supp_sec/7_additional_quantitative_results.tex}

\section{Training Procedure Study}

\Cref{tab:chunk-length-comparison} provides evidence supporting the effectiveness of our proposed training schedule.
We first train \ourmodel{} with three different chunk sizes
(i.e., sequences with $\{144, 48, 1\}$ frames), each with and without
the memory bank cache.
Training with long chunks (144 frames, \cref{tab:chunk-length-comparison}.1a) provides good performance
because there is a low gap between training and evaluation.
The cache provides no gains in this setting (\cref{tab:chunk-length-comparison}.1b) because the model already has memory proposals in most frames.
Training with shorter chunks (\cref{tab:chunk-length-comparison}.2a,3a) performs worse because there is a more significant gap between training and evaluation.
Including the cache helps significantly by closing the gap to evaluation but does not fully reach the long chunk performance (\cref{tab:chunk-length-comparison}.2b,3b).
As hypothesized in \cref{sec:method-training}, there is room for improvement by training with our proposed schedule and memory bank cache (\cref{tab:chunk-length-comparison}.4b). This strategy allows \ourmodel{} to learn generalized patterns over a diverse set of examples quickly by training on short chunks (more i.i.d. data) at the beginning when the learning rate is higher while refining its understanding on long chunks (closer to the deployment setting) towards the end when the learning rate is lower.
\Cref{tab:chunk-length-comparison}.4a shows the importance of the cache when using this training schedule; otherwise, training with small chunks is ineffective as the model would not learn to use the memory.

\input{tables/schedule_table.tex}


\subsection{Training Procedure Ablations}

\input{tables/more_training_ablations.tex}
In \cref{tab:more-training-ablations} we investigate
additional training procedures for \ourmodel{}.
For the experiments in this table we train for 45k iterations to reduce costs.
For fair comparisons, all methods in \cref{tab:more-training-ablations} were trained
with a fixed chunk length of 144 frames and no cache.
Row 3 uses the architecture of \ourmodel{} described in \cref{sec:method-arch}.
There are four alternative design questions we investigated:
\begin{itemize}
    \item If we accumulate gradients over the chunk length and update the model parameters once per chunk, does it improve performance?
    Our hypothesis was that this could reduce over-fitting to sequences of correlated training examples.
    However, comparing row 0 to row 3 of \cref{tab:more-training-ablations}, we find that
    accumulating gradients hurts performance.
    For this experiment, while we use the same number of model forward passes (45k), there are less model parameter updates (only once per chunk),
    resulting in an under-trained model, even if the learning dynamics are better.
    Training with 45k model parameter updates steps in this setting would multiply the training duration and cost by the chunk length, which is prohibitively expensive.
    \item Can we improve performance by initializing the memory proposal features $\mathbf{Q}^\mathrm{mem}$ with
    refinement features in the memory bank $\{\mathbf{Q}^\mathrm{ref}_{t - s_m}, \dots \mathbf{Q}^\mathrm{ref}_{t - s_m T_m}\}$? 
    Recall from \cref{sec:method-arch} that $\mathbf{Q}^\mathrm{mem}$ 
    is calculated from the boxes $\mathbf{B}^\mathrm{mem}$, confidence scores $\mathbf{C}^\mathrm{mem}$,
    and trajectory forecasts $\mathbf{T}^\mathrm{mem}$.
    However, the memory also stores past refined query features $\{\mathbf{Q}^\mathrm{ref}_{t - s_m}, \dots \mathbf{Q}^\mathrm{ref}_{t - s_m T_m}\}$, and
    our hypothesis was that initializing $\mathbf{Q}^\mathrm{mem}$ with these refined query features could improve performance
    because they contain richer learned information.
    To test this, we compute $\mathbf{Q}^\mathrm{mem}$ using $\mathbf{Q}^\mathrm{{ref}}_{t_m}$ and adding an encoding of
    the box, confidence score, and trajectory forecasts (the same way we computed the memory proposal features described in \cref{sec:method-arch}).
    However, comparing row 0 to row 3 of \cref{tab:more-training-ablations}, we find that using the refined query features
    does not improve performance over our proposed $\mathbf{Q}^\mathrm{mem}$ described in \cref{sec:method-arch}.
    We think this is because the distribution of these features is changing over training, which
    makes them difficult to learn with.
    \item To address the lack of improvement from using the refined features, we investigated using BPTT through these features
    to allow the model to learn to output refinement features that are relevant for future inferences.
    Due to GPU memory constraints, we could only back-propagate through one past inference.
    Unfortunately, we found that this did not improve performance significantly over not using BPTT (2 vs 1 in \cref{tab:more-training-ablations}),
    or over not using refinement features to initialize the memory features (2 vs 3 in \cref{tab:more-training-ablations}).
    We have two hypotheses for why this is: The first is that the position, size, confidence, and trajectory information in the memory features are important and easy
    for the refinement transformer to use, overpowering the information in the refinement features.
    Secondly, BPTT through one step might not be enough to see improvements.
    This is an area for future work.
\end{itemize}

% \ben{TODO: integrate these results throughout the paper!}

\input{sec/supp_sec/8_additional_qualitative_results.tex}


\input{sec/imp.tex}